### 2019-12-16 ic-journal/conclusions.tex
paper-pencil -> paper-and-pencil (appeared once in intro.tex)

The formalisation has focused on the theory of unique solution of
equations and contractions, both in the \univariate and in the
\multivariate cases. It has allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity.  The
formalisation brings up and exploits similarities between results and
proofs for different equivalences and preorders. Indeed we have
considered several ``unique-solution'' results (for various
equivalences and preorders); they share many parts of the proofs, but
present a few delicate and subtle differences in a few points. In a
paper-pencil proof, checking all details would be long and
error-prone, especially in cases where the proofs are similar to each
other or when there are long case analyses to be carried out.  We
believe that the formalisation of all definitions and theorems are
easy to read and to understand, as they are close to their original
statement in textbooks.

>>>>

The formalisation has focused on the theory of unique solution of
equations and contractions, both in the \univariate and in the
\multivariate cases. It has allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity.  The
formalisation brings up and exploits similarities between results and
proofs for different equivalences and preorders. Indeed we have
considered several ``unique-solution'' results (for various
equivalences and preorders); they share many parts of the proofs, but
present a few delicate and subtle differences in a few points. In a
paper-and-pencil proof, checking all details would be long and
error-prone, especially in cases where the proofs are similar to each
other or when there are long case analyses to be carried out.  We
believe that the formalisation of all definitions and theorems are
easy to read and to understand, as they are close to their original
statement in textbooks.
